Perceptions and Preferences for Meritocracy

### 2020-05-08 docs/paper.Rmd
paper
paper

---
title: "Perceptions and Preferences for Meritocracy"
css: "../input/css/custom.css"
linestretch: '1.5'
link-citations: yes
output:
    html_document:
        number_sections: true
        toc: true
        toc_float: true
        smart: false
linkcolor: blue
bibliography:
  - ../input/bib/EconomiaMoral.bib
  - ../input/bib/meritocracy.bib
editor_options:
  chunk_output_type: console
---

@@

```{r message=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
```

@@

Table 1: Model of perceptions and preferences for meritocracy and non-meritocracy

@@

### Table 2
![](../input/images/tabla2.png)

@@

### Diagram 1 
![](../input/images/app_mod.png)

@@

@@

4 XX producir tabla y llamar directamente desde la fuente o como imagen [__Pendiente__]

<!-- [Descriptive Table for the PPM-S, by group or the full sample] -->

```{r echo=FALSE}
load(file = "output/tables/sumdat04.RData");sumdat04
```

@@

5 XX Agregar gráficos de frecuencia , puede ser tipo trellis 2 x 4, arriba percepción abajo preferencias; la idea es generar un input más claro para la siguiente idea:

@@

```{r echo=FALSE}

load(file = "output/images/correlation.RData")
library(corrplot)
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r echo=FALSE}
load(file = "output/tables/tb.fm01.RData");tb.fm01
```

@@

Table 3: **Fit indicators**

|           | Model order 1 | Model order 2 | Model order 3 |
|:---------:|:-------------:|:-------------:|:-------------:|
| **n**     |      697      |      702      |      697      |
| **CFI**   |     0.997     |     0.984     |     0.991     |
| **TLI**   |     0.992     |     0.968     |     0.984     |
| **RMSEA** |     0.037     |     0.071     |     0.051     |
| **χ2**    |     28.03     |     64.156    |     39.090    |
| **p**     |      .000     |      .000     |      .000     |
| **χ2/gl** | 2,00          | 4,58          | 2,78          |

@@

@@

# Anexos

>>>>

---
title: "Perceptions and Preferences for Meritocracy"
css: "../input/css/custom.css"
linestretch: '1.5'
link-citations: yes
output:
  html_document:
    theme: flatly
    number_sections: true
    always_allow_html: yes
  pdf_document:
    keep_tex: false
    template: null
    number_sections: true
linkcolor: blue

bibliography:
  - ../input/bib/EconomiaMoral.bib
  - ../input/bib/meritocracy.bib
editor_options:
  chunk_output_type: console
---

@@

```{r message=FALSE, warning=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
#install.packages("captioner")
library(captioner)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
table_nums<-captioner(prefix = "Table")
plot_nums<-captioner(prefix = "Figure")
diam_nums<-captioner(prefix = "Diagram")
anx_nums<-captioner(prefix = "Annexed")

table_nums("ta", "Dimensions of meritocratic beliefs.")
table_nums("tb", "Items according to dimension.")
table_nums("tc", "Descriptive statistics of the scale.")
table_nums("td", "Factor loads and model fit.")
table_nums("te", "Comparison between model fit.")

diam_nums("da", "Survey flow")
diam_nums("db", "Theorical model")

plot_nums("fa", "Descriptive boxplot of the scale.")
plot_nums("fb", "Polychoric correlation.")

anx_nums("aa", "Representativeness of the sample.")
```

@@

`r table_nums("ta")`

@@

`r table_nums("tb")`

![](../input/images/tabla2.png)

@@

`r diam_nums("da")`

![](../input/images/app_mod.png)

@@

`r diam_nums("db")`

@@

<!-- [Descriptive Table for the PPM-S, by group or the full sample] -->
`r table_nums("tc")`

```{r echo=FALSE}
#load(file = "output/tables/sumdat04.RData");sumdat04
```

4 XX producir tabla y llamar directamente desde la fuente o como imagen [__Pendiente__]
5 XX Agregar gráficos de frecuencia , puede ser tipo trellis 2 x 4, arriba percepción abajo preferencias; la idea es generar un input más claro para la siguiente idea:

`r plot_nums("fa")`

@@

@@

`r plot_nums("fb")`

```{r echo=FALSE}
load(file = "output/images/correlation.RData")
library(corrplot)
corrplot(cor04$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

@@

`r table_nums("td")`

```{r echo=FALSE}
#load(file = "output/tables/tb.fm01.RData");tb.fm01
```

@@

`r table_nums("te")`

@@

# Anexos
`r anx_nums("aa")`
